Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-17 src/ms.tex
CMD edits

\begin{figure*}
    \includegraphics[width=\linewidth]{./figures/cmd.pdf}
    \caption{Color-magnitude diagram. The two panels are identical with exception of the orange points. In the background, a 2d histogram of the Kepler field, where darker values represent a higher density of stars, up to a threshold beyond which the highest density is saturated (shown in white). Shown by orange points are stars with photometric rotation period detections from either the \citet{McQuillan2014} or \citet{Santos2021} catalogs, on the left and right, respectively. The CKS long-period pile-up stars identified in this work are shown by black points. A Gaussian kernel density estimation of the \citet{Hall2021} asteroseismic sample is shown by black contours.}
    \label{fig:cmd}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{./figures/cmd.pdf}
    \caption{Color-magnitude diagram. The two panels are identical with exception of the orange points. In the background, a 2-d histogram of the Kepler field, where lighter shades represent a higher number of stars. Shown by orange points are stars with photometric rotation period detections from either the \citet{McQuillan2014} or \citet{Santos2021} catalogs, on the left and right, respectively. The CKS long-period pile-up stars identified in this work are shown by black points. A Gaussian kernel density estimation of the \citet{Hall2021} asteroseismic sample is shown by black contours.}
    \label{fig:cmd}
\end{figure*}
